Area maximisation in continuous time

### 2013-04-27 Notes/ContTime.tex
typo

Then, defining
%
\begin{equation}\label{eq:eigdiff}
  F_{ab} = \left\{
           \begin{aligned}
             &rt\,\e^{-q_art}, &\quad&\text{if } q_a=q_b,\\
             &\frac{\e^{-q_art}-\e^{-q_brt}}{q_b-q_a}, &&\text{otherwise,}
           \end{aligned}
           \right.
\end{equation}
%
we get
%
\begin{equation}\label{findiff}
\begin{aligned}
  \pdiff{\CL}{\M^\pm_{gh}} =&\,
    f^\pm \eq_g \prn{\brk{\fund \, \enc \, \e^{rt\frg} \w}_h - \brk{\fund \, \enc \, \e^{rt\frg} \w}_g} \\
    &\pm \eq_g \prn{\brk{\e^{rt\frg} \w}_h - \brk{\e^{rt\frg} \w}_g} \\
    &+ \sum_{ab} F_{ab} (\eq\enc\uv^a) \vv^{ag} (\uv^b_h-\uv^b_g) (\vv^a\w) \\
    &+ \mu^\pm_{gh} - \mu^\pm_{gg}.
\end{aligned}
\end{equation}
%

>>>>

Then, defining
%
\begin{equation}\label{eq:eigdiff}
  F_{ab} = \left\{
           \begin{aligned}
             &rt\,\e^{-q_art}, &\quad&\text{if } q_a=q_b,\\
             &\frac{\e^{-q_art}-\e^{-q_brt}}{q_b-q_a}, &&\text{otherwise,}
           \end{aligned}
           \right.
\end{equation}
%
we get
%
\begin{equation}\label{findiff}
\begin{aligned}
  \pdiff{\CL}{\M^\pm_{gh}} =&\,
    f^\pm \eq_g \prn{\brk{\fund \, \enc \, \e^{rt\frg} \w}_h - \brk{\fund \, \enc \, \e^{rt\frg} \w}_g} \\
    &\pm \eq_g \prn{\brk{\e^{rt\frg} \w}_h - \brk{\e^{rt\frg} \w}_g} \\
    &+ \sum_{ab} F_{ab} (\eq\enc\uv^a) \vv^a_g (\uv^b_h-\uv^b_g) (\vv^a\w) \\
    &+ \mu^\pm_{gh} - \mu^\pm_{gg}.
\end{aligned}
\end{equation}
%
